\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-01-18 papers/methods/paper.tex
Adding selection functions to paper

>>>>

\begin{figure}
	\begin{center}
		\includegraphics[width=\columnwidth]{DES3YR_DES_BHMEFF_AMG10.pdf}
		\includegraphics[width=\columnwidth]{DES3YR_LOWZ_BHMEFF_G10.pdf}
	\end{center}
	\caption{Fitting the selection function for both the DES 3YR spectroscopically confirmed supernova sample and the combined low-redshift sample. Blue errorbars represent the efficiency calculated by determining the ratio of discovered to generated supernovae in apparent magnitude bins for SNANA simulations. The black line represents the best fit analytic function for each sample, and the light grey lines surrounding the best fit value represent random realisations of analytic function taking into account uncertainty on the best fit value.}
	\label{fig:sf_snana}
\end{figure}
